Reintroduction of resistant frogs facilitates landscape-scale recovery in the presence of a lethal fungal disease

### 2024-09-28 doc/manuscript/translocation.qmd
Edits to render to latex
Use default cite method instead of natbib
Minor edits

---
format: pdf
#format:
#   latex: 
#      cite-method: natbib
include-in-header:
  text: |
    \usepackage{blkarray}
    \usepackage{lineno}\linenumbers
include-before-body: 
  text: |
    \captionsetup{format=plain, labelfont=bf, labelsep=space}
editor: visual
editor_options:
  markdown:
    wrap: sentence
crossref: 
  fig-title: "**Fig.**"
  fig-prefix: "Fig."
bibliography: translocation.bib
csl: nature.csl
link-bibliography: false
---

@@

### Figures and Legends

![**Conceptual model of Bd-caused decline and recovery in *R. sierrae*.** For the recovery portion, the model depicts both natural recovery and facilitated recovery via reintroductions, as well as the linkages between these two pathways. Rectangles and hexagons represent outcomes and processes, respectively. Blue text indicates components that are included in the current study. The general temporal scale of the depicted scenario is provided by the timeline, with the dashed portion indicating a projection into the future.](figures/conceptual_model.png){#fig-recovery-model width="95%"}

@@

![**Locations of translocated and donor *R. sierrae* populations.** All populations are in Yosemite National Park (park boundary indicated by black polygon). Symbol shapes indicate the donor population used for each translocation site, and 5-digit numbers identify each donor and translocation site. To obscure the exact locations of populations, random noise was added to all point coordinates. Inset map shows the location of Yosemite within California. In both maps, topography is shown with a grayscale hillshade layer, and elevation is indicated by colors layered over the hillshade. In the absence of hillshading, dark green colors indicate the lowest elevations and white indicates the highest elevation.](figures/map_translocation_points.png){#fig-yosemap width="60%"}

@@

![**1-year survival for each cohort of translocated frogs**. Median cohort-level survival was estimated for each of the 12 recipient sites using mrmr CMR models. Error bars show the 95% uncertainty intervals. Sites are arranged along the x-axis using the average of the median 1-year survival per translocation at each site. Dot colors indicate the donor population from which frogs in each translocated cohort were collected. When multiple translocations were conducted to a site, points and error bars are slightly offset to avoid overlap.](figures/translocation_survival_bysiteid.png){#fig-translocation-survival width="60%"}

@@

![**Conditional effects of predictors of 1-year frog survival**. Results are from the among-site meta-analysis and 1-year frog survival is expressed as a probability. **a** winter severity in the year following translocation, **b** elevation of recipient site, **c** donor population, and **d** sex. In (a) and (b), blue lines are medians and gray ribbons are 95% uncertainty intervals for the posterior distributions of the predicted effects. In (c) and (d), box plots show medians (horizontal line), first and third quartiles (hinges), largest and smallest values within 1.5x interquartile range (whiskers), and values outside the 1.5x interquartile range (dots) for the posterior distributions of the predicted effects.](figures/cond_effects_plot.png){#fig-cond-effects width="80%"}

@@

![**Estimated growth rates and extinction probabilities of reintroduced populations**. **a** Predicted long-run growth rate $\lambda$ for different values of yearly adult survival probability $\sigma_{A_R}$ and year-1 juvenile survival probability $\sigma_{J_1}$, given the parameterized, deterministic model. Colored points show the predicted $\lambda$ values for the twelve translocated populations when year-1 juvenile survival probability is $\sigma_{J_1} = 0.10$ (indicated by the dashed line). The red line shows where $\lambda = 1$. Note that the point for 70413 is mostly hidden behind other points. **b** Predicted 50-year extinction probabilities of the 12 reintroduced populations, given demographic stochasticity, environmental variability in $\sigma_{J_1}$, and different mean values of $\sigma_{J_1}$. There are 6 lines at extinction probability = 1, 5 of which (70414--70619) are partially or completely hidden beneath the line for 70505. **c** 100 simulated trajectories (black lines) from the population viability model that most closely matched the observed abundance trajectory of adult amphibians at site 70550 (light orange).](figures/pop_viability_figures_for_manuscript.png){#fig-viability width="95%"}

>>>>

---
#format: pdf
format:
   latex 
#      cite-method: natbib
include-in-header:
  text: |
    \usepackage{blkarray}
    \usepackage{lineno}\linenumbers
include-before-body: 
  text: |
    \captionsetup{format=plain, labelfont=bf, labelsep=space}
editor: visual
editor_options:
  markdown:
    wrap: sentence
crossref: 
  fig-title: "**Fig.**"
  fig-prefix: "Fig."
bibliography: translocation.bib
csl: nature.csl
link-bibliography: false
---

@@

### Figures and Figure Legends

![**Conceptual model of Bd-caused decline and recovery in *R. sierrae*.** For the recovery portion, the model depicts both natural recovery and facilitated recovery via reintroductions, as well as the linkages between these two pathways. Rectangles and hexagons represent outcomes and processes, respectively. Blue text indicates components that are included in the current study. The general temporal scale of the depicted scenario is provided by the timeline, with the dashed portion indicating a projection into the future.](submission_files/figures/conceptual_model_180mm.pdf){#fig-recovery-model}

@@

![**Locations of translocated and donor *R. sierrae* populations.** All populations are in Yosemite National Park (park boundary indicated by black polygon). Symbol shapes indicate the donor population used for each translocation site, and 5-digit numbers identify each donor and translocation site. To obscure the exact locations of populations, random noise was added to all point coordinates. Inset map shows the location of Yosemite within California. In both maps, topography is shown with a grayscale hillshade layer, and elevation is indicated by colors layered over the hillshade. In the absence of hillshading, dark green colors indicate the lowest elevations and white indicates the highest elevation.](submission_files/figures/map_translocation_points_88mm.pdf){#fig-yosemap}

@@

![**1-year survival for each cohort of translocated frogs**. Median cohort-level survival was estimated for each of the 12 recipient sites using mrmr CMR models. Error bars show the 95% uncertainty intervals. Sites are arranged along the x-axis using the average of the median 1-year survival per translocation at each site. Dot colors indicate the donor population from which frogs in each translocated cohort were collected. When multiple translocations were conducted to a site, points and error bars are slightly offset to avoid overlap.](submission_files/figures/translocation_survival_bysiteid_88mm.pdf){#fig-translocation-survival}

@@

![**Conditional effects of predictors of 1-year frog survival**. Results are from the among-site meta-analysis and 1-year frog survival is expressed as a probability. **a** winter severity in the year following translocation, **b** elevation of recipient site, **c** donor population, and **d** sex. In (a) and (b), blue lines are medians and gray ribbons are 95% uncertainty intervals for the posterior distributions of the predicted effects. In (c) and (d), box plots show medians (horizontal line), first and third quartiles (hinges), largest and smallest values within 1.5x interquartile range (whiskers), and values outside the 1.5x interquartile range (dots) for the posterior distributions of the predicted effects.](submission_files/figures/conditional_effects_plot_88mm.pdf){#fig-cond-effects}

@@

![**Estimated growth rates and extinction probabilities of reintroduced populations**. **a** Predicted long-run growth rate $\lambda$ for different values of yearly adult survival probability $\sigma_{A_R}$ and year-1 juvenile survival probability $\sigma_{J_1}$, given the parameterized, deterministic model. Colored points show the predicted $\lambda$ values for the twelve translocated populations when year-1 juvenile survival probability is $\sigma_{J_1} = 0.10$ (indicated by the dashed line). The red line shows where $\lambda = 1$. Note that the point for 70413 is mostly hidden behind other points. **b** Predicted 50-year extinction probabilities of the 12 reintroduced populations, given demographic stochasticity, environmental variability in $\sigma_{J_1}$, and different mean values of $\sigma_{J_1}$. There are 6 lines at extinction probability = 1, 5 of which (70414--70619) are partially or completely hidden beneath the line for 70505. **c** 100 simulated trajectories (black lines) from the population viability model that most closely matched the observed abundance trajectory of adult amphibians at site 70550 (light orange).](submission_files/figures/pop_viability_figures_for_manuscript_180mm.pdf){#fig-viability}

### 2024-09-28 doc/manuscript/translocation.tex
Minor edits

\includegraphics[width=0.95\textwidth,height=\textheight]{figures/conceptual_model.png}

@@

\includegraphics[width=0.6\textwidth,height=\textheight]{figures/map_translocation_points.png}

@@

\includegraphics[width=0.6\textwidth,height=\textheight]{figures/translocation_survival_bysiteid.png}

@@

\includegraphics[width=0.8\textwidth,height=\textheight]{figures/cond_effects_plot.png}

@@

\includegraphics[width=0.95\textwidth,height=\textheight]{figures/pop_viability_figures_for_manuscript.png}

>>>>

\includegraphics{submission_files/figures/conceptual_model_180mm.pdf}

@@

\includegraphics{submission_files/figures/map_translocation_points_88mm.pdf}

@@

\includegraphics{submission_files/figures/translocation_survival_bysiteid_88mm.pdf}

@@

\includegraphics{submission_files/figures/conditional_effects_plot_88mm.pdf}

@@

\includegraphics{submission_files/figures/pop_viability_figures_for_manuscript_180mm.pdf}
